---
title: "Network Meta-analysis and meta-regression for the secondary outcome of efficacy: DO"
subtitle: Prepared by Konstantina on 11 October, refers to the analysis of secondary outcome - DO in both frequentist and Bayesian setting
output:
  word_document:
    fig_height: 7
    fig_width: 10
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA1=read_excel("C:/Users/kc19o338/Desktop/Schizophrenia project/Documentation of Schizophrenia relapses/Analysis schizofrenia/Datasets/dataset_relapse_oral and depot pooled.xlsx", na="99999")
DATA1<-DATA1[,-1]
```
#Delete studies

I excluded all the studies that did not have the N_DO_AnyReason
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA<-DATA1[!is.na(DATA1$N_DO_AnyReason),]
unique(DATA1[is.na(DATA1$N_DO_AnyReason),]$Final_ID_all)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
excludeID <-c(4330,4334,4360,4373,4380,4416,4478,4588)
DATA=DATA[!DATA$Final_ID_all%in%excludeID,]
cat("The 1-arm studies that were excluded are the following:",excludeID)
```
#Description of the network

Below is a description for the network formed by studies examining the outcome DO

Below are the total number of participants in each of the included drug
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#describe the data
tapply(DATA$N_randomized,DATA$Drug_name,sum,na.rm=T)

```

Number of studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(length(table(DATA$Study_name)))
```
Number of drugs:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
length(unique(DATA$Drug_name))
```
Number of arms in our studies
```{r, echo=FALSE, message=FALSE, warning=FALSE}
table(table(DATA$Final_ID_all))
```

The network consists of 79 two-arm studies and 3 three-arm studies.

The plot below shows the available data

```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name, event=N_DO_AnyReason, n=N_randomized, data=DATA, sm="OR", studlab=Final_ID_all, allstudies = TRUE)

#run NMA and create an object called EFF for efficacy
net1<-netmeta(TE, seTE, treat1, treat2, studlab, data = DATApairs, sm = "OR", comb.random=TRUE, comb.fixed=FALSE, prediction=TRUE, ref="Placebo")

```


```{r, echo=FALSE}

#network plot
netgraph(net1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

#FREQUENTIST SETTING

#Network meta-analysis 

Below are the relative treatment effects from the NMA model. 
The first graph presents the sorted ORs, whereas the second graph presents the ORs in the same order as in the Bayesian setting later 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(net1, ref="Placebo", sortvar = -Pscore,xlab="OR",xlim=c(0.01,5))

forest(net1, ref="Placebo", xlab="OR",xlim=c(0.01,5))
```


The P-scores (equivalent to the SUCRAs) are shown below
```{r, echo=FALSE}
netrank(net1)
```


The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(net1$tau,3)))
```

and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(net1$I2,3)*100,"%"))
```


There is important evidence of inconsistency in the data. 
There are 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
split=netsplit(net1) 
SIDEp=split$compare.random$p
SIDEp=SIDEp[!is.na(SIDEp)]
#proportion of inconsistent loops
cat(length(SIDEp))
```

comparisons in the network that can be detached, and there is inconsistency (according to SIDE p-value<0.10) in

```{r, echo=F, message=FALSE, warning=FALSE}
cat(length(SIDEp[SIDEp<=0.1]))
```
loops which gives a % of inconsistent comparisons equal to
```{r, echo=F, message=FALSE, warning=FALSE}
cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%"))
```


The p-value from the design-by-treatment test is

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a=decomp.design(net1)
print(round(a$Q.inc.random$pval,3))
```

Because p-value < 0.10 and the incosistent comparisons > 10%, it is not recommended to perform NMA even with pooled data.

#BAYESIAN SETTING

# Network meta-analysis

The names of drugs are recoded properly for the analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}
NMAdataBinary=make.jagsNMA.data(studyid=Final_ID_all,t=Drug_name,r=N_DO_AnyReason,n=N_randomized,data=DATA,type="binary",reference = "Placebo")

```


The Network meta-analysis and its results
```{r, echo=FALSE, message=FALSE, warning=FALSE}

NMAinJAGSBinP <- jags.parallel(data = NMAdataBinary, inits = NULL, 
                               parameters.to.save = c("ORref","tau"), n.chains = 2, n.iter = 120000,
                               n.burnin = 10000,DIC=F,n.thin=10,
                               model.file = modelNMABinary)
print(NMAinJAGSBinP)


```

The prior of tau that was used is a positive normal distribution (0,1). 

```{r, include=FALSE}
traceplot(NMAinJAGSBinP)
```

#Comparison between frequentist ORs and Bayesian ORs 

```{r, include=FALSE}
ORFrequentist<-exp(net1$TE.random[,dimnames="Placebo"])
ORFrequentist<-as.data.frame(ORFrequentist)
ORFrequentist<-as.data.frame(ORFrequentist[-15,])
ORunadjustedBayesian<-NMAinJAGSBinP$BUGSoutput$mean$ORref
ORunadjustedBayesian<-as.data.frame(ORunadjustedBayesian)
ORcomparison<-cbind(ORFrequentist,ORunadjustedBayesian)
colnames(ORcomparison)<-c("Frequentist", "Bayesian")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ORcomparison
```
