---
title: "Network Meta-analysis and meta-regression for the secondary outcome of efficacy: Overall Symptoms"
subtitle: Prepared by Konstantina on 11 October, refers to the analysis in both frequentist and Bayesian setting
output:
  word_document:
    fig_height: 7
    fig_width: 10
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA1=read_excel("C:/Users/kc19o338/Desktop/Schizophrenia project/Documentation of Schizophrenia relapses/Analysis schizofrenia/Datasets/dataset_relapsefinal.xlsx", na="99999")
DATA1<-DATA1[,-1]
```
#Delete studies

I excluded all the studies that did not have information about OverallSymptoms_participants, OverallSymptoms_mean or OverallSymptoms_sd
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA<-DATA1[!is.na(DATA1$OverallSymptoms_participants),]
DATA<-DATA[!is.na(DATA$OverallSymptoms_mean),]
DATA<-DATA[!is.na(DATA$OverallSymptoms_sd),]
```

#Description of the network

Below is a description for the network formed by studies examining the secondary outcome of efficacy Overall Symptoms.

Below are the total number of participants in each of the included drug
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#describe the data
tapply(DATA$OverallSymptoms_participants,DATA$Drug_name,sum,na.rm=T)

```
Number of drugs
```{r, echo=FALSE, message=FALSE, warning=FALSE}
length(unique(DATA$Drug_name))
```
Number of studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(length(table(DATA$Study_name)))
```

Number of arms in our tudies
```{r, echo=FALSE, message=FALSE, warning=FALSE}
table(table(DATA$Final_ID_all))
```
The network consists of 42 two-arm studies and 2 three-arm studies.

The plot below shows the available data

```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name, mean=OverallSymptoms_mean, sd=OverallSymptoms_sd, n=OverallSymptoms_participants, data=DATA, sm="SMD", studlab=Final_ID_all, allstudies = TRUE)

#run NMA and create an object called EFF for efficacy
net1<-netmeta(TE, seTE, treat1, treat2, studlab, data = DATApairs, sm = "SMD", comb.random=TRUE, comb.fixed=FALSE, prediction=TRUE, ref="Placebo oral or depot")
```


```{r, echo=FALSE}

#network plot
netgraph(net1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

#FREQUENTIST SETTING

#Network meta-analysis 

Below are the relative treatment effects from the NMA model. 
The first graph presents the sorted SMDs, whereas the second graph presents the SMDs in the same order as in the Bayesian setting later 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(net1, ref="Placebo oral or depot", sortvar = -Pscore,xlab="OR")

forest(net1, ref="Placebo oral or depot", xlab="OR")
```


The P-scores (equivalent to the SUCRAs) are shown below
```{r, echo=FALSE}
netrank(net1)
```


The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(net1$tau,3)))
```

and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(net1$I2,3)*100,"%"))
```


There is little evidence of inconsistency in the data. There are in total

```{r, echo=FALSE, message=FALSE, warning=FALSE}
split=netsplit(net1) 
SIDEp=split$compare.random$p
SIDEp=SIDEp[!is.na(SIDEp)]
#proportion of inconsistent loops
cat(length(SIDEp))
```

comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in

```{r, echo=F, message=FALSE, warning=FALSE}
cat(length(SIDEp[SIDEp<=0.1]))
```
loops which gives a % of inconsistent loops equal to
```{r, echo=F, message=FALSE, warning=FALSE}
cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%"))
```
We need to acknowledge though that the network is very very thin. So, the power of the test is certainty very low. 


The p-value from the design-by-treatment test is

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a=decomp.design(net1)
print(round(a$Q.inc.random$pval,3))
```
#BAYESIAN SETTING

# Network meta-analyis

The names of drugs are recoded properly for the analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}
NMAdataContinuous=make.jagsNMA.data(studyid=Final_ID_all,t=Drug_name,y=OverallSymptoms_mean, sd=OverallSymptoms_sd, n=OverallSymptoms_participants,data=DATA,type="cont",reference = "Placebo oral or depot")

```


The Network meta-analysis and its results
```{r, echo=FALSE, message=FALSE, warning=FALSE}

NMAinJAGSBinP <- jags.parallel(data = NMAdataContinuous, inits = NULL, 
                               parameters.to.save = c("SMD.ref","tau"), n.chains = 2, n.iter = 120000,
                               n.burnin = 10000,DIC=F,n.thin=10,
                               model.file = modelNMAContinuous)
print(NMAinJAGSBinP)


```
The prior of tau that was used is uniform distribution (0,5)

```{r, include=FALSE}
traceplot(NMAinJAGSBinP)
```


```{r, include=FALSE}
NMAinJAGSBinP <- jags.parallel(data = NMAdataContinuous, inits = NULL, 
                               parameters.to.save = c("SMD.ref","tau","SMD"), n.chains = 2, n.iter = 120000,
                               n.burnin = 10000,DIC=F,n.thin=10,
                               model.file = modelNMAContinuous)

leaguetable=out.jagsNMA.results(NMAinJAGSBinP,parameter="SMD",treatnames = sort(unique(DATA$Drug_name)),forestplot=F)
leaguetableEFF=as.data.frame(leaguetable$leaguetable)
leaguetableEFF
```

#Comparison between frequentist SMDs and Bayesian SMDs 

```{r, include=FALSE}
SMDFrequentist<-(net1$TE.random[,dimnames="Placebo oral or depot"])
SMDFrequentist<-as.data.frame(SMDFrequentist)
SMDunadjustedBayesian<-NMAinJAGSBinP$BUGSoutput$mean$SMD.ref
SMDunadjustedBayesian<-as.data.frame(SMDunadjustedBayesian)
SMDcomparison<-cbind(SMDFrequentist,SMDunadjustedBayesian)
colnames(SMDcomparison)<-c("Frequentist", "Bayesian")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
SMDcomparison
```
