---
title: "Network Meta-analysis for the secondary outcome of efficacy: Social Functioning"
subtitle: Prepared by Konstantina on 30 October, refers to the analysis in both frequentist and Bayesian setting
output:
  word_document:
    fig_height: 7
    fig_width: 10
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA1=read_excel("C:/Users/kc19o338/Desktop/Schizophrenia project/Documentation of Schizophrenia relapses/Analysis schizofrenia/Datasets/dataset_relapse_oral and depot pooled.xlsx", na="99999")
DATA1<-DATA1[,-1]
```
#Delete studies

I excluded all the studies that did not have any information about SocialFunctioning_participants, SocialFunctioning_mean or SocialFunctioning_sd
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DATA<-DATA1[!is.na(DATA1$SocialFunctioning_participants),]
DATA<-DATA[!is.na(DATA$SocialFunctioning_mean),]
DATA<-DATA[!is.na(DATA$SocialFunctioning_sd),]


excludeID <-c(4330,4360,4380)
DATA=DATA[!DATA$Final_ID_all%in%excludeID,]
cat("Because of single-arm studies, the following studies were excluded:",excludeID)
```

#Description of the network

Below is a description for the network formed by studies examining the secondary outcome of efficacy Social Functioning

Below are the total number of participants in each of the included drug
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#describe the data
tapply(DATA$SocialFunctioning_participants,DATA$Drug_name,sum,na.rm=T)

```
Number of drugs
```{r, echo=FALSE, message=FALSE, warning=FALSE}
length(unique(DATA$Drug_name))
```
Number of studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(length(table(DATA$Study_name)))
```

Number of arms in our tudies
```{r, echo=FALSE, message=FALSE, warning=FALSE}
table(table(DATA$Final_ID_all))
```

The network consists of 18 two-arm studies.

The plot below shows the available data

```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name, mean=SocialFunctioning_mean, sd=SocialFunctioning_sd, n=SocialFunctioning_participants, data=DATA, sm="SMD", studlab=Final_ID_all, allstudies = TRUE)

#run NMA and create an object called EFF for efficacy
#run NMA and create an object called EFF for efficacy
net1<-netmeta(TE, seTE, treat1, treat2, studlab, data = DATApairs, sm = "SMD", comb.random=TRUE, comb.fixed=FALSE, prediction=TRUE, ref="Placebo")
#netconnection(treat1,treat2,studlab,data=DATApairs)
```


```{r, echo=FALSE}

#network plot
netgraph(net1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

#FREQUENTIST SETTING

#Network meta-analysis 

Below are the relative treatment effects from the NMA model. 
The first graph presents the sorted SMDs, whereas the second graph presents the SMDs in the same order as in the Bayesian setting later 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(net1, ref="Placebo", sortvar = -Pscore,xlab="SMD")

forest(net1, ref="Placebo", xlab="SMD")
```


The P-scores (equivalent to the SUCRAs) are shown below
```{r, echo=FALSE}
netrank(net1)
```


The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(net1$tau,3)))
```

and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(net1$I2,3)*100,"%"))
```


There is important evidence of inconsistency in the data. There are

```{r, echo=FALSE, message=FALSE, warning=FALSE}
split=netsplit(net1) 
SIDEp=split$compare.random$p
SIDEp=SIDEp[!is.na(SIDEp)]
#proportion of inconsistent loops
cat(length(SIDEp))
```

comparisons in the network that can be detached, and there is inconsistency (according to SIDE p-value<0.10) in

```{r, echo=F, message=FALSE, warning=FALSE}
cat(length(SIDEp[SIDEp<=0.1]))
```
comparisons which gives a % of inconsistent comparisons equal to
```{r, echo=F, message=FALSE, warning=FALSE}
cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%"))
```


The p-value from the design-by-treatment test is

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a=decomp.design(net1)
print(round(a$Q.inc.random$pval,3))
```
The p-value is lower than 0.10 and the inconsistency of the comparisons are really high (57.1%). NMA is not recommended for this network.

#BAYESIAN SETTING

# Network meta-analysis

The names of drugs are recoded properly for the analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}
NMAdataContinuous=make.jagsNMA.data(studyid=Final_ID_all,t=Drug_name,y=SocialFunctioning_mean, sd=SocialFunctioning_sd, n=SocialFunctioning_participants,data=DATA,type="cont",reference = "Placebo")

```


The Network meta-analysis and its results
```{r, echo=FALSE, message=FALSE, warning=FALSE}

NMAinJAGSBinP <- jags.parallel(data = NMAdataContinuous, inits = NULL, 
                               parameters.to.save = c("SMD.ref","tau"), n.chains = 2, n.iter = 120000,
                               n.burnin = 10000,DIC=F,n.thin=10,
                               model.file = modelNMAContinuous)
print(NMAinJAGSBinP)


```
The prior of tau that was used is uniform distribution (0,5)

```{r, include=FALSE}
traceplot(NMAinJAGSBinP)
```


```{r, include=FALSE}
NMAinJAGSBinP <- jags.parallel(data = NMAdataContinuous, inits = NULL, 
                               parameters.to.save = c("SMD.ref","tau","SMD"), n.chains = 2, n.iter = 120000,
                               n.burnin = 10000,DIC=F,n.thin=10,
                               model.file = modelNMAContinuous)

leaguetable=out.jagsNMA.results(NMAinJAGSBinP,parameter="SMD",treatnames = sort(unique(DATA$Drug_name)),forestplot=F)
leaguetableEFF=as.data.frame(leaguetable$leaguetable)
leaguetableEFF
```

#Comparison between frequentist SMDs and Bayesian SMDs 

```{r, include=FALSE}
SMDFrequentist<-(net1$TE.random[,dimnames="Placebo"])
SMDFrequentist<-as.data.frame(SMDFrequentist)
SMDunadjustedBayesian<-NMAinJAGSBinP$BUGSoutput$mean$SMD.ref
SMDunadjustedBayesian<-as.data.frame(SMDunadjustedBayesian)
SMDcomparison<-cbind(SMDFrequentist,SMDunadjustedBayesian)
colnames(SMDcomparison)<-c("Frequentist", "Bayesian")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
SMDcomparison
```
